### 2018-08-30 paper/finitecomplete-failures.tex
Proof of lemma on partitions improved.

\begin{lemma}\label{lemma:minhitmax}
Let $n\ge 2$ be any positive integer.
We call a sequence $a_1\le a_2\le \ldots\le  a_{\alpha}, a_i\in \mathbb{N}, i=1,\dots, \alpha$, a partion of $n$, if $n=\Sigma_{i=1}^{\alpha}a_i$.
Define
$$p(n)=\begin{cases} 3^k &\text{if}\,\, n=3k\\ 2^2\cdot 3^{k-1} &\text{if}\,\, n=3k+1\\2\cdot 3^{k} &\text{if}\,\, n=3k+2\end{cases}$$
Then  $$p(n)=\max\big\{\prod_{i=1}^{\alpha}a_i~|~n=\Sigma_{i=1}^{\alpha}a_i,\ a_i,
\alpha\in \mathbf{N}\big\}$$
\end{lemma}
\begin{proof}
Let $n\ge 2$.
Obviously, 
\begin{equation}\label{eq:1} 
   n\le p(n).
\end{equation}
We show that
$p(n)$ is associated with a unique partition  $b_1\le b_2\le \ldots\le  b_{\beta}$ of $n$ with $b_i\in \{2,3\}, i=1,\dots,\beta$. We denote this partition  by $\pi(n)$. 
To prove its existence, 
let $a_1, \ldots , a_{\alpha}$ be an {\it arbitrary} partition of $n$. 
Suppose there is some $a_j$, $1\le j\le \alpha$, with $a_j>3$. Then from~(\ref{eq:1}) we have 
$$
\prod_{i=1}^{\alpha}a_i\le a_1\cdot a_{j-1}\cdot p(a_j)\cdot a_{j+1}\ldots\cdot a_{\alpha}$$
Hence, if we replace $a_j$ by $p(a_j)$, the new partition has a product which is
 not less than the original partition $a_1, \ldots , a_{\alpha}$, but the value $a_j$
 is now represented by smaller numbers. This process is repeated until there is a partition of $n$ with maximal product such that every term is $2$ or $3$.
Since $6=2+2+2=3\cdot 3$ and $2^3< 3^2$, the number of $2$s in such maximal partition is less than $2$. This shows that $\pi(n)$ is uniquely determined.

Let $a_1\le a_2\le \ldots\le  a_{\alpha}$ with $a_i\in \{2,3\}, i=1,\dots,\alpha$, be a partition of $n$ with maximal product. Let $k_1\le 2$ be the number of terms equal $2$ and $k_2$ be the number of terms equal $3$.
Then $n=2k_1+3k_2$ and  $n\equiv 2k_1 (\mod 3)$ with $k_1\le 2$. Then

\begin{align*}
k_1&=
\begin{cases} 
0 &\text{if}\,\, \exists k: n=3k\\ 
2 &\text{if}\,\, \exists k: n=3k+1\\
1 &\text{if}\,\, \exists k: n=3k+2
\end{cases}\\
 k_2&=
 \begin{cases} 
 k &\text{if}\,\, n=3k\\ 
 k-1 &\text{if}\,\, n=3k+1\\
 k &\text{if}\,\, n=3k+2\end{cases}
\end{align*}
% 
 and  
 $$
 \prod_{i=1}^{\alpha}a_i=2^{k_1}\cdot 3^{k_2}=
 \begin{cases} 
 3^k &\text{if}\,\,  n=3k\\ 
 2^2\cdot 3^{k-1} &\text{if}\,\,   n=3k+1\\
 2\cdot 3^{k} &\text{if}\,\,  n=3k+2\end{cases}
 $$
 \xbox
 \end{proof}
%
From Lemma~\ref{lemma:minhitmax}, we conclude that 
$$h=\begin{cases} 
3^{|\frac{\Sigma}{3}|} &\text{if}\,\, \exists k: |\Sigma|=3k\\ 
2^2\cdot 3^{\frac{|\Sigma|-4}{3}} &\text{if}\,\, \exists k : |\Sigma| =3k+1\\
2\cdot 3^{\frac{|\Sigma| - 2}{3}} &\text{if}\,\, \exists k: |\Sigma| =3k+2
\end{cases}
$$

>>>>

\begin{lemma}\label{lemma:minhitmax}
Let $n\ge 2$ be any positive integer.
We call a sequence $0 < a_1\le a_2\le \ldots\le  a_{\alpha}, a_i\in \mathbb{N}, i=1,\dots, \alpha$, a partion of $n$, if $n=\Sigma_{i=1}^{\alpha}a_i$.
Define
$$p(n)=\begin{cases} 3^k &\text{if}\,\, n=3k\\ 2^2\cdot 3^{k-1} &\text{if}\,\, n=3k+1\\2\cdot 3^{k} &\text{if}\,\, n=3k+2\end{cases}$$
Then  $$p(n)=\max\big\{\prod_{i=1}^{\alpha}a_i~|~n=\Sigma_{i=1}^{\alpha}a_i,\ a_i,
\alpha\in \mathbb{N}\big\}.$$
\end{lemma}
\begin{proof}
Let $n\ge 2$.
Obviously, \begin{equation}\label{eq:1} n\le p(n).\end{equation}
Define $\pi(n)$ to be the following partition  of $n$: 
$$\pi(n)=\begin{cases} \underbrace{3,\ldots,3}_{k\text{ times}}  &\text{if}\,\, n=3k\\ 2,2,\underbrace{3,\ldots,3}_{k-1\text{ times}}  &\text{if}\,\, n=3k+1\\2,\underbrace{3,\ldots,3}_{k\text{ times}}  &\text{if}\,\, n=3k+2\end{cases}$$
Then the product of the numbers in 
$\pi(n)$ equals  $p(n)$. In the remainder of the proof
we have to show that $p(n)$ is really maximal in the sense of the lemma.

Since the number of partitions of a given $n$ is finite, $\text{max}\{\prod_{i=1}^{\alpha}a_i~|~n=\Sigma_{i=1}^{\alpha}a_i, a_i\in \mathbb{N}\}$ exists.

Let $a_1, \ldots , a_{\alpha}$ be any partition of $n\ge 2$ with maximal product. Then,
obviously,  $a_i>1$ for all $i=1,\dots,\alpha$.
Suppose there is some $a_j$, $1\le j\le \alpha$, with $a_j>3$. Then from~(\ref{eq:1}) we have 
$$\prod_{i=1}^{\alpha}a_i\le a_1\cdot a_{j-1}\cdot p(a_j)\cdot a_{j+1}\ldots\cdot a_{\alpha}.$$
Hence we can replace $a_j$ by $\pi(a_j)$, and the new partition has  a product value
which is not less then the original partition $a_1, \ldots , a_{\alpha}$. This process
can be repeated, until every $a_i$ in the resulting partition is either 2 or 3.
Hence there exists a partition of $n$ with maximal product, such that every term is $2$ or $3$.
Since $6=2+2+2=3\cdot 3$ and $2^3< 3^2$, the number of $2$'s in such a maximal partition is less than $3$. 
Let $a_1\le a_2\le \ldots\le  a_{\alpha}$ with $a_i\in \{2,3\}, i=1,\dots,\alpha$, be a partition of $n$ with maximal product. Let $k_1\le 2$ be the number of terms equal $2$ and $k_2$ be the number of terms equal $3$.
Every $n\ge 2$ can be represented by $n=2k_1+3k_2$, $n\equiv 2k_1 (\mod 3)$ with $k_1\le 2$, and $\prod_{i=1}^{\alpha}a_i=2^{k_1}\cdot 3^{k_2}$. We have

\begin{align*}k_1&=\begin{cases} 0 &\text{if}\,\, n=3k\\ 2 &\text{if}\,\, n=3k+1\\1 &\text{if}\,\, n=3k+2\end{cases}\\
 k_2&=\begin{cases} k &\text{if}\,\, n=3k\\ k-1 &\text{if}\,\, n=3k+1\\k &\text{if}\,\, n=3k+2\end{cases}\\
\prod_{i=1}^{\alpha}a_i&=\begin{cases} 3^k &\text{if}\,\, n=3k\\ 2^2\cdot 3^{k-1} &\text{if}\,\, n=3k+1\\2\cdot 3^{k} &\text{if}\,\, n=3k+2\end{cases}\end{align*}
This proves the lemma.
\xbox
\end{proof}
%
From Lemma~\ref{lemma:minhitmax}, we conclude that 
$$h=\begin{cases} 
3^{|\frac{\Sigma}{3}|} &\text{if}\,\, \exists k: |\Sigma|=3k\\ 
2^2\cdot 3^{\frac{|\Sigma|-4}{3}} &\text{if}\,\, \exists k : |\Sigma| =3k+1\\
2\cdot 3^{\frac{|\Sigma| - 2}{3}} &\text{if}\,\, \exists k: |\Sigma| =3k+2
\end{cases}
$$
